R Notebook

### 2019-07-15 src/testing_file.Rmd
fecky feck violin plots

>>>>

# violin plots

```{r}
#load a test raster

ras <- raster("../output/maxent/predictions/apr/cloglog_st201004000120.asc")
plot(ras)
ras2 <- raster("../output/maxent/predictions/oct/cloglog_st201010000120.asc")
plot(ras2)
rasd <- as.data.frame(ras)
rasd$month <- "4"
rasd2 <- as.data.frame(ras2)
rasd2$month <- "10"
names(rasd)[names(rasd) == "cloglog_st201004000120"] <- "prob"
names(rasd2)[names(rasd2) == "cloglog_st201010000120"] <- "prob"
rasd$month <- as.factor(rasd$month)
rasd2$month <- as.factor(rasd2$month)
rd <- rbind(rasd, rasd2)
rd
p <- ggplot(rd, aes(x=month, y = prob)) + geom_violin(trim=FALSE)
plot(p)

mth <- c("jan", "mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec")
for (m in 1:length(mth)){
  mon <- mth[m]
  vlst <- list.files(paste0("../output/maxent/predictions/", mon), pattern = "^avg_cloglog.*.asc", full.names = TRUE)
  for (v in 1:length(vlst)){
    ras <- raster(vlst[v])
    rasd <- as.data.frame(ras)
    if (mon == "jan"){
      rasd$month <- "1"
      rnm <- names(ras)
      names(rasd)[names(rasd) == rnm] <- "prob"
      rasd$month <- as.factor(rasd$month)
      rd1 <- rasd
      } else if(mon == "mar"){
        rasd$month <- "3"
        rnm <- names(ras)
        names(rasd)[names(rasd) == rnm] <- "prob"
        rasd$month <- as.factor(rasd$month)
        rd3 <- rasd
      } else if(mon == "apr"){
        rasd$month <- "4"
        rnm <- names(ras)
        names(rasd)[names(rasd) == rnm] <- "prob"
        rasd$month <- as.factor(rasd$month)
        rd4 <- rasd
      } else if(mon == "may"){
        rasd$month <- "5"
        rnm <- names(ras)
        names(rasd)[names(rasd) == rnm] <- "prob"
        rasd$month <- as.factor(rasd$month)
        rd5 <- rasd
      } else if(mon == "jun"){
        rasd$month <- "6"
        rnm <- names(ras)
        names(rasd)[names(rasd) == rnm] <- "prob"
        rasd$month <- as.factor(rasd$month)
        rd6 <- rasd
      } else if(mon == "jul"){
        rasd$month <- "7"
        rnm <- names(ras)
        names(rasd)[names(rasd) == rnm] <- "prob"
        rasd$month <- as.factor(rasd$month)
        rd7 <- rasd
      } else if(mon == "aug"){
        rasd$month <- "8"
        rnm <- names(ras)
        names(rasd)[names(rasd) == rnm] <- "prob"
        rasd$month <- as.factor(rasd$month)
        rd8 <- rasd
      } else if(mon == "sep"){
        rasd$month <- "9"
        rnm <- names(ras)
        names(rasd)[names(rasd) == rnm] <- "prob"
        rasd$month <- as.factor(rasd$month)
        rd9 <- rasd
      } else if(mon == "oct"){
        rasd$month <- "10"
        rnm <- names(ras)
        names(rasd)[names(rasd) == rnm] <- "prob"
        rasd$month <- as.factor(rasd$month)
        rd10 <- rasd
      } else if(mon == "nov"){
        rasd$month <- "11"
        rnm <- names(ras)
        names(rasd)[names(rasd) == rnm] <- "prob"
        rasd$month <- as.factor(rasd$month)
        rd11 <- rasd
      } else if(mon == "dec"){
        rasd$month <- "12"
        rnm <- names(ras)
        names(rasd)[names(rasd) == rnm] <- "prob"
        rasd$month <- as.factor(rasd$month)
        rd12 <- rasd
      }

      rd <- cbind(rd1, rd3, rd4, rd5, rd6, rd7, rd8, rd9, rd10, rd11, rd12)
    #rd <- as.data.frame(rd)
    #rd$month <- as.factor(rd$month)
  }

p <- ggplot(rd2, aes(x=month, y = prob)) + geom_violin(trim=FALSE)
plot(p)

}
